Tor's Usability for Censorship Circumvention

### 2015-12-10 paper/circumvention-experiment.tex
Fix link to prototype
Add images of new interface

However, other elements of the process can be automated without adverse effects.
For example, local proxy settings can be imported from other browsers on the
machine by looking for settings in well-known locations on the filesystem. Automatically
detecting the need for a proxy and importing the proxy settings required would save
our participants from a task they do not have the background to easily complete. 
Since this piece of automation offers a significant increase in usability for our users
(addressing our most common failure case) with no apparent risks, we have incorporated it
into our design. \\

@@

We chose to display all information about bridges and proxies is now contained on one 
respective screen in the interface, giving the user has the full context of their decision.
We made the guidance from the last interface (to not choose a bridge, to not choose a proxy)
more direct by selecting the  option to opt out of a proxy as the default option on those screens. 
This results in a more streamlined interface with fewer windows
and fewer clicks required for our participants. \\

@@

A clear example of this is the ``Connect'' button on the first screen, which has
increased in size and become green, making it more prominent as the recommended
option. We believe that this will help the majority of Tor users. 
Although some of our participants in environments had chosen to connect
directly when they needed to configure, this is generally seen as low-risk today, and 
the majority of censorship today can be circumvented with a direct connection. 
A similar aesthetic applies to the connect button seen after custom
configuration.

To help lessen the cognitive load and distribute a representative amount of space
for options, recommendations are selected as the default option, and rarely used 
elements are deemphasized. To encourage our users to click on helpful options, 
the help button on the bridge configuration screen
has been emphasized to be bigger, since it is a helpful option which people rarely
clicked. To discourage our users from using an advanced setting only technical users 
have a chance of  configuring correctly and should only be used in very rare circumstances, 
we have now incorporated the custom bridge configuration in the dropdown menu; 
it previously took up a significant portion of the bridge configuration screen.

@@

@@

@@

\section{Resources}
\noindent Our online artifacts of the work done during this class, Fall 2015,
are below: 
\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
\item \href{https://github.com/lindanlee/circumvention-ux-tor}{github repo with experiment plans, code, videos, interviews, and much more}
\item \href {a clickable prototype of our interface redesign}{https://marvelapp.com/15a2294}
\item \href{https://github.com/lindanlee/circumvention-ux-tor/tree/master/sessions/pre/videos}{qualitative interface evaluation videos}
\item \href{https://github.com/lindanlee/circumvention-ux-tor/blob/master/sessions/pre/participant-summaries.txt}{summaries of qualitative interface evaluation videos}
\item \href{https://github.com/lindanlee/circumvention-ux-tor/tree/master/sessions/pre/notes}{qualitative interface evaluation interview notes}
\item \href{https://github.com/lindanlee/circumvention-ux-tor/blob/master/setup/setup-environment}{experimental setup code: firewall and screen capture} 
\item \href{https://github.com/lindanlee/circumvention-ux-tor/blob/master/setup/takedown-environment}{experimental takedown code: saving files and cleanup} 
\end{itemize}

>>>>

However, other elements of the process can be automated without adverse effects.
For example, local proxy settings can be imported from other browsers on the
machine by looking for settings in well-known locations on the filesystem. Automatically
detecting the need for a proxy and importing the proxy settings required would save
our participants from a task they do not have the background to easily complete. 
Since this piece of automation offers a significant increase in usability for our users
(addressing our most common failure case) with no apparent risks, we have incorporated it
into our design (Figure \ref{fig:redesign-proxy}). \\

\begin{figure}[h]
\label{fig:redesign-proxy}
  \centering
    \includegraphics[width=0.5\textwidth]{redesign-proxy.png}
    \caption{the proxy configuration screen, with an option to automatically
        ``Import from another browser''}
\end{figure}

@@

We chose to display all information about bridges and proxies is now contained on one 
respective screen in the interface, giving the user has the full context of their decision.
We made the guidance from the last interface (to not choose a bridge, to not choose a proxy)
more direct by selecting the  option to opt out of a proxy as the default option on those screens
(Figure \ref{fig:redesign-noproxy}).
This results in a more streamlined interface with fewer windows
and fewer clicks required for our participants. \\

\begin{figure}[h]
\label{fig:redesign-noproxy}
  \centering
    \includegraphics[width=0.5\textwidth]{redesign-noproxy.png}
    \caption{The default option is now to ``Proceed without proxy settings.''}
\end{figure}

@@

A clear example of this is the ``Connect'' button on the first screen
\ref{fig:redesign-firstscreen}, which has
increased in size and become green, making it more prominent as the recommended
option. We believe that this will help the majority of Tor users. 
Although some of our participants in environments had chosen to connect
directly when they needed to configure, this is generally seen as low-risk today, and 
the majority of censorship today can be circumvented with a direct connection. 
A similar aesthetic applies to the connect button seen after custom
configuration.

\begin{figure}[h]
\label{fig:redesign-firstscreen}
  \centering
    \includegraphics[width=0.5\textwidth]{redesign-firstscreen.png}
    \caption{the initial connection screen. Note the prominence given to the
    ``Connect'' button.}
\end{figure}

To help lessen the cognitive load and distribute a representative amount of space
for options, recommendations are selected as the default option, and rarely used 
elements are deemphasized. To encourage our users to click on helpful options, 
the help button on the bridge configuration screen
has been emphasized to be bigger, since it is a helpful option which people rarely
clicked. To discourage our users from using an advanced setting only technical users 
have a chance of  configuring correctly and should only be used in very rare circumstances, 
we have now incorporated the custom bridge configuration in the dropdown menu
(Figure \ref{fig:redesign-bridges});
it previously took up a significant portion of the bridge configuration screen.

\begin{figure}[h]
\label{fig:redesign-bridges}
  \centering
    \includegraphics[width=0.5\textwidth]{redesign-bridges.png}
    \caption{the bridge selection screen, with the option to ``Add Custom
    Bridge''}
\end{figure}

@@

\begin{figure}[h]
\label{fig:redesign-waiting}
  \centering
    \includegraphics[width=0.5\textwidth]{redesign-waiting.png}
    \caption{the new connection screen}
\end{figure}

@@

\begin{figure}[h]
\label{fig:redesign-failure}
  \centering
    \includegraphics[width=0.5\textwidth]{redesign-failure.png}
    \caption{the screen displayed when a connection failed}
\end{figure}

@@

\section{Resources}
\noindent Our online artifacts of the work done during this class, Fall 2015,
are below: 
\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
\item \href{https://github.com/lindanlee/circumvention-ux-tor}{github repo with experiment plans, code, videos, interviews, and much more}
\item \href{https://marvelapp.com/15a2294}{a clickable prototype of our interface redesign}
\item \href{https://github.com/lindanlee/circumvention-ux-tor/tree/master/sessions/pre/videos}{qualitative interface evaluation videos}
\item \href{https://github.com/lindanlee/circumvention-ux-tor/blob/master/sessions/pre/participant-summaries.txt}{summaries of qualitative interface evaluation videos}
\item \href{https://github.com/lindanlee/circumvention-ux-tor/tree/master/sessions/pre/notes}{qualitative interface evaluation interview notes}
\item \href{https://github.com/lindanlee/circumvention-ux-tor/blob/master/setup/setup-environment}{experimental setup code: firewall and screen capture} 
\item \href{https://github.com/lindanlee/circumvention-ux-tor/blob/master/setup/takedown-environment}{experimental takedown code: saving files and cleanup} 
\end{itemize}
